---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
Make sure you install the following packages:

- knitr
- rmarkdown
- ggplot2
- plyr (just in case :-) 
- 

Let's read in the file and convert the date column to an actual date type.

```{r loaddata, echo=TRUE, message=FALSE, warning=FALSE}
library (plyr)
library (ggplot2)
library (knitr)
library (rmarkdown)

activity <- read.csv("activity.csv")
activity$date <- as.Date(activity$date, "%Y-%m-%d")
head(activity)
```
We've got N/As but we'll deal with them later. 

We should be ready for some analysis now. 

## What is mean total number of steps taken per day?

First we will calcualte the total number of steps taken per day and generate a histogram. 


```{r, echo=TRUE, message=FALSE, warning=FALSE}
stepsperday <- ddply(activity, .(date), summarize, total = sum(steps, na.rm=TRUE))
hist(stepsperday$total, col="red", xlab = "Total steps per day", main="Histogram of total steps per day")
meanperday <- sprintf ("%.2f", mean(stepsperday$total, na.rm=TRUE))
medianperday <- median(stepsperday$total, na.rm=TRUE)
```

The mean number of steps/day was `r meanperday`.
The median number of steps/day was `r medianperday`.

## What is the average daily activity pattern?

First aggregate things by 5 minute interval. Then generate the line chart.

```{r, echo=TRUE, message=FALSE, warning=FALSE}
stepsper5min <- ddply(activity, .(interval), summarize, mean = mean(steps, na.rm=TRUE))
plot ( stepsper5min, type="l", col="purple", main="Average steps/5 min interval", xlab="5 minute interval", ylab="Mean steps taken")
topsteps <- head(stepsper5min[order(stepsper5min$mean, decreasing=TRUE),], 1)
```

Interval `r topsteps[1,1]` contains the maximum average number of steps `r sprintf ("%.f", topsteps[1,2])`.

## Inputing missing values
```{r, echo=TRUE, message=FALSE, warning=FALSE}

```




## Are there differences in activity patterns between weekdays and weekends?
```{r, echo=TRUE, message=FALSE, warning=FALSE}

```

