---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
Make sure you install the following packages:

- knitr
- rmarkdown
- ggplot2
- plyr (just in case :-) 

Let's read in the file and convert the date column to an actual date type.

```{r loaddata, echo=TRUE, message=FALSE, warning=FALSE}
library (plyr)
library (ggplot2)
library (knitr)
library (rmarkdown)

activity <- read.csv("activity.csv")
activity$date <- as.Date(activity$date, "%Y-%m-%d")
head(activity)
```
We've got N/As but we'll deal with them later. 

We should be ready for some analysis now. 

## What is mean total number of steps taken per day?
```{r, echo=TRUE, message=FALSE, warning=FALSE}

```


## What is the average daily activity pattern?
```{r, echo=TRUE, message=FALSE, warning=FALSE}

```




## Imputing missing values
```{r, echo=TRUE, message=FALSE, warning=FALSE}

```




## Are there differences in activity patterns between weekdays and weekends?
```{r, echo=TRUE, message=FALSE, warning=FALSE}

```

